Bird beak's elaboration and exploration

### 2021-11-01 Analysis/03.1-results.Rmd
updated to dispRity syntax

```{r, eval = TRUE, echo = FALSE}
## Load the covar
load(file = "../Data/Processed/allbirds_8748t_8Dshapespace_31levels.rda")
## Load the data
load(file = "../Data/Processed/form_shape_space_1tree_2levels.rda")
shapespace <- form_shape_space_1tree_2levels$shape_space
## Loading the group names
load("../Data/Processed/group_names_level_1_2.rda")

superorder_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = allbirds_8748t_8Dshapespace_31levels,
      group         = MCMCglmm.levels(allbirds_8748t_8Dshapespace_31levels)[c(1:8, 32)],
      rename.groups = c(names(group_names_level_1_2), "phylogeny")[c(1:8, 32)])

order_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = allbirds_8748t_8Dshapespace_31levels,
      group         = MCMCglmm.levels(allbirds_8748t_8Dshapespace_31levels)[-c(1:8, 33)],
      rename.groups = c(names(group_names_level_1_2), "phylogeny")[-c(1:8,33)])
```

```{r, message = FALSE, warning = FALSE, fig.height = 5, fig.width = 5, echo = FALSE}
## Plotting just the space
sauron.plot(superorder_shapespace,
            main = "Shapespace",
            cex = 0.5,
            legend = FALSE)
```
The global Shape space

```{r, echo = FALSE, fig.height = 18, fig.width = 18, eval = FALSE}
par(mfrow = c(2,2))
## Plotting mean axes
sauron.plot(superorder_shapespace,
            col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
            main = "Average ellipses by super order",
            ellipses = mean,
            legend = FALSE,
            points = FALSE,
            cex = 0.5)
## Plotting mean ellipses
sauron.plot(superorder_shapespace,
            col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
            main = "Average major axes by super order",
            major.axes = mean,
            legend = TRUE,
            points = FALSE,
            cex = 0.5)
## Plotting mean axes
sauron.plot(order_shapespace,
            col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
            main = "Average ellipses by order",
            ellipses = mean,
            legend = FALSE,
            points = FALSE,
            cex = 0.5)
## Plotting mean ellipses
sauron.plot(order_shapespace,
            col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
            main = "Average major axes by order",
            major.axes = mean,
            legend = TRUE,
            points = FALSE,
            cex = 0.5)
```
Main axes and ellipses visualisation

@@

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}
## Run the analyses between groups
super_results_between <- covar.projections.wrapper(superorder_shapespace,
                                             type = "between",
                                             base = "phylogeny",
                                             dispRity.out = TRUE)
## Run the analyses between groups
order_results_between <- covar.projections.wrapper(order_shapespace,
                                             type = "between",
                                             base = "phylogeny",
                                             dispRity.out = TRUE)
## Run the analyses of groups on the phylogeny
super_results_phylo <- covar.projections.wrapper(superorder_shapespace,
                                            type = "within",
                                            base = "phylogeny",
                                            incl.base = TRUE,
                                            dispRity.out = TRUE,
                                            verbose = TRUE)
## Run the analyses of groups on the phylogeny
order_results_phylo <- covar.projections.wrapper(order_shapespace,
                                            type = "within",
                                            base = "phylogeny",
                                            incl.base = TRUE,
                                            dispRity.out = TRUE,
                                            verbose = TRUE)
## Run the analyses groups on themselves
super_results_within <- covar.projections.wrapper(superorder_shapespace,
                                            type = "within",
                                            dispRity.out = TRUE,
                                            verbose = TRUE)
## Run the analyses groups on themselves
order_results_within <- covar.projections.wrapper(order_shapespace,
                                            type = "within",
                                            dispRity.out = TRUE,
                                            verbose = TRUE)
## Save all
allbirds_8748t_8Dshapespace_31levels_results_list <- list(
        "super_results_between" = super_results_between,
        "order_results_between" = order_results_between,
        "super_results_phylo"   = super_results_phylo,
        "order_results_phylo"   = order_results_phylo,
        "super_results_within"  = super_results_within,
        "order_results_within"  = order_results_within)
save(allbirds_8748t_8Dshapespace_31levels_results_list, file = "../Data/Processed/allbirds_8748t_8Dshapespace_31levels_results_list.rda")
```

```{r, echo = FALSE}
## Quick load
load(file = "../Data/Processed/allbirds_8748t_8Dshapespace_31levels_results_list.rda")
results <- allbirds_8748t_8Dshapespace_31levels_results_list
```

>>>>

```{r, eval = TRUE, echo = FALSE}
## Load the data
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")
## Select the data
shapespace <- shapespace_allbirds_lvl_superorder_order[[1]]$space
## Load the covar
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")

superorder_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(1:8, 32)],
      rename.groups = c(levels(shapespace$level1)[-1], "phylogeny")) #[-1] is because the first level is ""

order_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[-c(1:8, 33)],
      rename.groups = c(levels(shapespace$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
```

```{r, message = FALSE, warning = FALSE, fig.height = 5, fig.width = 5, echo = FALSE}
## Plotting just the space
covar.plot(superorder_shapespace,
           main = "Shapespace",
           cex = 0.5,
           legend = FALSE)
```
The global Shape space

```{r, echo = FALSE, fig.height = 18, fig.width = 18, eval = FALSE}
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
## Plotting mean axes
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
```
Main axes and ellipses visualisation

@@

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}
## Run the analyses between groups
super_results_between <- dispRity.covar.projections(superorder_shapespace,
                                             type = "groups",
                                             base = "phylogeny")
## Run the analyses between groups
order_results_between <- dispRity.covar.projections(order_shapespace,
                                             type = "groups",
                                             base = "phylogeny")
## Run the analyses of groups on the phylogeny
super_results_phylo <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE)
## Run the analyses of groups on the phylogeny
order_results_phylo <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE)
## Run the analyses groups on themselves
super_results_within <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            verbose = TRUE)
## Run the analyses groups on themselves
order_results_within <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            verbose = TRUE)
## Save all
shapespace_allbirds_lvl_superorder_order_results_list <- list(
        "super_results_between" = super_results_between,
        "order_results_between" = order_results_between,
        "super_results_phylo"   = super_results_phylo,
        "order_results_phylo"   = order_results_phylo,
        "super_results_within"  = super_results_within,
        "order_results_within"  = order_results_within)
save(shapespace_allbirds_lvl_superorder_order_results_list, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
```

```{r, echo = FALSE}
## Quick load
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
```
